### 2014-07-16 paper_skeleton.tex
im about to rewrite the paper_skeleton quite a bit

\section{Abstract}
Learning usually occurs in noisy environments.  In order to make a decision, one must accumulate the  evidence for different alternatives and choose one only once the uncertainty about the choice is sufficiently reduced.  There are two equivalent mathematical formulations of the optimal decision making algorithm: a sequential probability ratio test in which the likelihoods of two hypotheses are evaluated as more data points are collected and a drift-diffusion stochastic differential equation in which the belief about two hypotheses does a random walk until a threshold is reached.  In the random walk formulation, the threshold dictating when a decision has been made affects both the accuracy of the decision and the expected time until a decision is reached.  If the utility of a decision depends on accuracy and decision time, the threshold can be optimized accordingly.  There are two biological systems in which the variables used to make a decision can be described by a random walk: the firing rates of neural populations in the brain of an individual making a decision about a visual stimulus and the beliefs of monkeys about their relative dominance based on the fights they have engaged in.  The stochastic differential equations used to model these quite different systems are nearly identical, which suggests that there are universal principles underlying learning through noisy dynamical systems in biology.  However, there are (at least) three significant differences between the two models.  First, whereas in the neural system, the differential equations are often reduced to a one-dimensional model, the social system is inherently two-dimensional.  Second, in the social system, there is a strategic component to the system since the optimal threshold of one animal depends on the threshold of the other animal, whereas in the neural system both neural populations are part of the cognitive system of the same individual trying to optimize its decision making.  Relatedly, the output of the decision has additional strategic consequences in the social system.    Finally, in the social system, a monkey is not only trying to make a decision about his dominance with respect to one other monkey, but he is additionally trying to make decisions about many other partners at once, whereas in the neural case there is only one decision to be made at a time.  First, we found that the dimensionality of the decision process does not affect its accuracy.  The costs of the waiting time until a decision affect the Nash equilibrium thresholds for a pair of animals, the optimal thresholds for a group of animals, and the skewness and information content of the resulting distribution of power.  In comparing the output of the model of the social system to data, we found that ...

@@

Similar models have previously been applied to animal conflicts, although in that case the animals had perfect memory of their past interactions \citep{Froment:2010fk}

@@

@@

The quality of the decision process depends on each of these three quantities.  The lower the decision time and error rate, the better the decision.  However, both cannot be decreased simultaneously so there is a tradeoff that depends on how the two quantities are prioritized.  Additionally, in the social case, each animal may benefit from lower its signaling probability, which may or may not conflict with lowering the error rate, depending on whether the animal is weaker or stronger than its opponent.  To quantify the utility of the decision process, we introduce three weights, $w_1$, $w_2$, and $w_3$, which determine how the three quantities are prioritized.  For animal $i$, we define
\begin{equation*}
U_i=w_1\text{DT}+w_2\text{ER}+w_3\text{SP}_i.
\end{equation*}
The decision is better if $U_i$ is lower.  In the social system, $w_2$ can be interpreted as the cost of fighting since when $w_2$ is higher, the time spent fighting until a decision is reached is more costly.  Similarly, $w_3$ can be interpreted as the benefit from being the dominant animal in a pair.

@@

@@

\subsection{Decisions are as accurate without an arbiter. }
We compare the decision making process in the full two-dimensional system and in a reduced one-dimensional system to see whether decisions are made more accurately or quickly in one or the other.  To make the systems directly comparable, we assume in both cases that the thresholds are symmetric, i.e. $T_1=T_2$.

We find that the two-dimensional decision is as accurate as the one-dimensional decision.  That is, for a given expected time to reach a decision, the two-dimensional decision will reach the correct decision with the same probability.  Accuracy decreases as leak rates ($\ell$) become higher, but increases when the strength of the input ($c$) is higher (Figure \ref{2dacc}).

@@

\subsection{Strategic Decision Making }
Differences in the thresholds could be explained by individual variation.  However, there may be a strategic aspect to this variation in the social system.  In the neural system, an individual wants to make both a decision that is both quick and accurate.  This is also true in the social system.  However, it may also be the case that a monkey wants to avoid emitting a subordination signal and wants to receive a signal, regardless of whether or not this is the ``correct" outcome, i.e. whether or not he is actually more likely to win a fight.  The criterion used to optimize the threshold, therefore, may be quite different in the two systems.  Additionally, the speed and outcome of the decision process depend on both animals' thresholds.  Since an animal's best behavior depends on the behavior of the other animal, optimizing the threshold is strategic in the social system but not in the neural system.

For any pair of individuals, each has a Nash equilibrium threshold such that, if they choose those thresholds, neither has an incentive to choose another.  These thresholds depend on the relative dominance of the two animals and how costly waiting is.  If waiting is not costly and the error rate does not matter ($w_1=0$, $w_2=0$, $w_3>0$), there is no incentive for the individuals to stop accumulating evidence (fighting, in the social case) so they will set high thresholds in order to wait until the other individual gives up.  However, as waiting costs increase, the pair can reach a decision more quickly if the weaker individual lowers its threshold.  If waiting costs are high enough, the stronger individual will also lower its threshold to avoid a long decision time (Figure \ref{nasheq_thresholds}).  By increasing the costs of waiting, the weaker individual has an incentive to give up more quickly, which can actually improve the accuracy of the decision process (Figure \ref{nasheq_thresholds}).  For low to moderate waiting costs, pairs of individuals making a difficult decision (low $c$, e.g. animals with similar fighting abilities) will take longer to reach a decision than pairs making a difficult decision (high $c$, e.g. animals with disparate fighting abilities).  However, when costs are high, the pairs that take the longest to reach a decision are those making moderately difficult decisions (Figure \ref{nasheq_thresholds}).  This is because pairs making difficult decisions will both set their thresholds quite low and in pairs making difficult decisions the weaker will set its threshold much lower, both of which decrease the time it takes until reaching a decision.

\subsection{Costs affect the shape and the information content of the power distribution.  }
A monkey can try to decide whether it is more or less likely to win a fight than another monkey using information from the fights the pair has previously engaged in.  Further, he can try to make such a decision about every other member of its social group.  Since he is trying to use the same algorithm to learn about every other animal, he is constrained to have only one decision threshold for each of these decision processes.  The optimal decision threshold in this social context depends on the distribution of fighting abilities in the group and the decision thresholds of the other animals.

When waiting for a decision becomes more costly ($c_2$ increases), the resulting distribution of the number of signals received first becomes more skewed, with a heavier right tail, and then loses it skewness again (Figure \ref{power}). Changing $c_1$ and $c_3$ have less of an effect, although when $c_1$ is higher the skewness slightly increases.

@@

\begin{figure}
\includegraphics[width=\textwidth]{2d_accuracy.pdf}
\caption{\label{2dacc} }
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{2d_flexible_thresholds.pdf}
\caption{\label{2dflex} When the two thresholds in the two-dimensional system are allowed to vary freely, the decision process can be arbitrarily accurate in a given amount of time, depending on how much lower the weaker animal's threshold is than the stronger animal's threshold.  The expected time to reach a decision is on the x-axis and the probability of reaching the correct decision in that amount of time is on the y-axis.  The curve depends on the ratio of the weaker animal's threshold to the stronger animal's threshold ($\rho$).  Lower ratios are represented in higher darker curves.}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{nasheq_thresholds.pdf}
\caption{\label{nasheq_thresholds} If a pair of individuals optimize their thresholds in response to each other, as the costs of waiting increase, first the weaker individual will start to lower his threshold to avoid waiting for a long time and then the stronger individual will start to lower his threshold as well.  As the costs of waiting increase, first the accuracy with which a pair can make a difficult decision increases and then it decreases.  At low waiting costs, difficult decisions take the most time.  At intermediate costs, intermediate decisions take the most time.  At high costs, easy decisions take the most time. The first row of panels shows the Nash equilibrium thresholds as a function of the difficulty of the decision ($c$ close to $.5$ is a more difficult decision).  The second and third rows show, respectively, the probability of the pair reaching the correct decision and the expected time until a decision is reached, if the pair of individuals uses the Nash equilibrium thresholds.  Each column corresponds to a particular waiting cost and the cost increases from left to right ($w_1=0, w_3=1-w_2$).  }
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{groupeq_thresholds.pdf}
\caption{\label{groupeq_thresholds} If the animals optimize their thresholds with respect to the thresholds and fighting abilities of the whole group of animals, as the costs of fighting increase, first the weaker animals in the group lower their thresholds to avoid fighting for a long time with the stronger animals and then the stronger animals lower their thresholds as well.  The ability of to learn from an animal's signaling behavior decreases as the costs of fighting increase. When fighting is not costly, the pairs of animals that take longest to decide on a relationship are those with similar fighting abilities. As costs increase pairs of animals with similarly low fighting abilities resolve their relationships quickly, whereas pairs of animals with similarly high fighting abilities take a long time to resolve their relationships.  The first row of panels shows the optimal threshold as a function of the animal's true rank with respect to fighting ability.  The second row shows the mutual information between the probability of emitting a signal and the probability of being the weaker animal, as a function of the animal's true rank.  The third row shows the expected time until each pair of animals resolves their relationship.  Each column corresponds to a particular waiting cost and the cost increases from left to right ($w_1=0, w_3=1-w_2$).   }
\end{figure}

\begin{figure}
\begin{subfigure}{3.415in}
\caption{}
\includegraphics[width=\textwidth]{skewness_heatmap.pdf}
\end{subfigure}
\begin{subfigure}{3.415in}
\caption{}
\includegraphics[width=\textwidth]{mutinfo_heatmap.pdf}
\end{subfigure}
\caption{\label{power} As the costs of waiting increase, the distribution of the number of relationships in which an animal is dominant becomes skewed to the right and then loses its skewness as costs increase further.  As the costs of waiting increase, the information content of the power distribution always decreases and if dominance is more important than accuracy the information content is higher.  The simplex shows the possible combinations of priorities, $w_1$, $w_2$, and $w_3$ such that the three weights sum to $1$.  In the lower left corner, $w_1=1$ (only accuracy matters), in the upper corner $w_2=1$ (only waiting time matters), and in the lower right $w_3=1$ (only the probability of receiving the signal matters).  The heatmaps show (a) the skewness of the power distribution and (b) the mutual information of the power distribution when the animals in the group optimize their thresholds according to those weights.  
%Increasing or decreasing $c_2$ has the strongest effect.  Increasing $c_1$ slightly increases the skewness. 
}
\end{figure}

\begin{table}
\centering
\caption{\label{variables}{\bf  Variables and interpretations in neural and social systems.} }
\ra{1.3}
\begin{tabular}{@{}rllll@{}}
Variable & Interpretation & Neural &   Social \\
\cmidrule{1-4} 
& input & dots moving left or right & fights won or lost
\\$c$ & strength of input & coherence of dots & probability of stronger animal winning
\\$X_1,X_2$ & decision variables &  firing rates of neural populations & opinions about relative dominance
\\ & dist. of states of the world & left / right equally likely & distribution of fighting abilities
\\ & decision & subject indicates left or right & one animal emits a subordination signal
\\ & correct decision & subject chooses correct direction & weaker animal signals
\end{tabular}
\end{table}

\begin{table}\centering
\caption{\label{models}{\bf  Comparison of models applied to neural and social systems.} Differences are highlighted in red.}
\ra{1.3}
\begin{tabular}{@{}rllll@{}}
& \multicolumn{2}{c}{Neural} &  Social \\
\cmidrule{2-3} \cmidrule{4-4} 
%model  & DDM or OU & race && race with leak
%\\
dimensionality & $1$  && $2$
\\decision & difference hits a threshold  && \fcolorbox{red}{white}{one var. hits a threshold}
\\ optimality criterion &  reward from being ``right" && reward from being ``right"
\\ & reward rate && reward rate
\\ & Bayes risk && Bayes risk
\\ & && \fcolorbox{red}{white}{reward from  receiving signal}
\\optimization depends on & input strength && input strength
\\ & noise && noise
\\ & leak rate && leak rate
\\ & && \fcolorbox{red}{white}{other animal's threshold}
\\threshold  algorithm & error correction
\\  & hill climbing
\end{tabular}
\end{table}

>>>>

\section{Abstract}
Learning usually occurs in noisy environments.  In order to make a decision, one must accumulate the  evidence for different alternatives and choose one only once the uncertainty about the choice is sufficiently reduced.  There are two biological systems in which the variables used to make a decision can be described by a random walk: the firing rates of neural populations in the brain of an individual making a decision about a visual stimulus and the beliefs of monkeys about their relative dominance based on the fights they have engaged in.  The same stochastic differential equations can be used to model these quite different systems, which suggests that there are universal principles underlying learning through noisy dynamical systems.  In the neural system, the differential equations are often reduced to a one-dimensional model, but the social system is inherently two-dimensional.  The thresholds dictating when a decision has been made affect both the accuracy of the decision and the expected time until a decision is reached. We find that the dimensionality of the decision process does not affect its accuracy.  We find that if a pair of individuals optimize their thresholds to avoid waiting, a pair making an easy decision will take more time than a pair making a difficult decision.  In a group of individuals optimizing their thresholds to avoid waiting, those pairs making the difficult decisions about high value inputs will have to wait the longest.  Finally, the skewness of the power distribution in the social system is maximized at intermediate waiting costs and the information content of the power distribution is higher when the individual maximize their probability of becoming dominant rather than the accuracy of their decisions. In comparing the output of the model of the social system to data, we found that ...

@@

Similar models have previously been applied to animal conflicts, although in that case the model assumed that the animals had perfect memory of their past interactions \citep{Froment:2010fk}

@@

%In the neural system, an individual wants to make both a decision that is both quick and accurate.  This is also true in the social system.  However, it may also be the case that a monkey wants to avoid emitting a subordination signal and wants to receive a signal, regardless of whether or not this is the ``correct" outcome, i.e. whether or not he is actually more likely to win a fight.  The criterion used to optimize the threshold, therefore, may be quite different in the two systems.  Additionally, the speed and outcome of the decision process depend on both individuals' thresholds.  Since an individuals' best behavior depends on the behavior of the other animal, optimizing the threshold has a strategic aspect.

@@

The quality of the decision process depends on each of these three quantities.  The lower the decision time and error rate, the better the decision.  However, both cannot be decreased simultaneously so there is a tradeoff that depends on how the two quantities are prioritized.  Additionally, in the social case, each animal may benefit from lower its signaling probability, which may or may not conflict with lowering the error rate, depending on whether the animal is weaker or stronger than its opponent.  To quantify the utility of the decision process, we introduce three weights, $w_1$, $w_2$, and $w_3$, which determine how the three quantities are prioritized.  For animal $i$, we define
\begin{equation*}
U_{i}=w_1\text{DT}+w_2\text{ER}+w_3\text{SP}_i.
\end{equation*}
The decision is better if $U_i$ is lower.  In the social system, $w_2$ can be interpreted as the cost of fighting since when $w_2$ is higher, the time spent fighting until a decision is reached is more costly.  Similarly, $w_3$ can be interpreted as the benefit from being the dominant animal in a pair.

@@

\subsection{Optimal thresholds }
An individual-- either a neural population or a monkey-- can be engaged in either a single decision or in many decisions at once.  In the social system, for example, an animal wants to decide whether it is dominant or subordinate to every other member of its social group.  For any pair of individuals, each has a utility, $U_1$ and $U_2$, and consequently each has a Nash equilibrium threshold such that, if they choose those thresholds, neither has an incentive to choose another.  Similarly, in a group of individuals, each animal $i$ has a utility $U_{ij}$ from its decision process with animal $j$.  These lead to an optimized set of thresholds such that no individual has an incentive to choose another threshold.

Since an individual is trying to use the same algorithm to learn about every other animal, he is constrained to have only one decision threshold for each of these decision processes.  The optimal decision threshold in this group context depends on the distribution of difficulties ($c$) of the decision an individual will have to make and the thresholds of the other individuals.  In the social system, the distribution of difficulties ($c$) comes from the distribution of fighting abilities of the animals.

 We use the following procedure to find optimal thresholds as a function of position in the group.  We repeatedly draw a set of fighting abilities from a uniform distribution; we find the optimal thresholds for each set, and then find the average optimal threshold as a function of an animal's order in the set of fighting abilities. To find the optimal thresholds for a given set of fighting abilities, we turn the difference in fighting abilities between each pair into the difficulty of the decision they have to make ($c$).  For an initial set of thresholds, we find $U_{ij}$ for each animal $i$ in each of its decisions and then average $\langle U_{ij}\rangle_j$ across all the animals with which it is engaged in a decision process.  We then allow each animal to choose a threshold that optimizes $\langle U_{ij}\rangle_j$ with respect to the rest of the group's thresholds and we iterate these choices until no animal chooses a new threshold.

\subsection{Consensus }
Consensus about the value of each individual in a group emerges out of the decision process.  In the social system, an animal's social power depends on the consensus in the group about its fighting ability \cite{Flack:2004oq,Flack:2006uq,Brush:2013fk}.  Given the decisions that each pair of individuals reaches, there are measures of the consensus in the group that successfully predict an animal's social power and also extend to other social systems \cite{Brush:2013fk}.  For each random set of fighting abilities, we let the animals optimize their thresholds, which give the probability that each pair will reach either decision, and we then generate a set of decisions given by these probabilities.  These decisions then give a distribution of power among the group.  For many random sets of fighting abilities, we can find the mutual information between the power distribution and the true fighting abilities, which we call the information content of the power distribution. It tells us how informative observing the outcomes of the decisions is about the underlying fighting abilities.  We also find the average skewness of the power distributions.

@@

\subsection{Decisions are as accurate without an arbiter. }
We compare the decision making process in the full two-dimensional system and in a reduced one-dimensional system to see whether decisions are made more accurately or quickly in one or the other.  To make the systems directly comparable, we assume in both cases that the thresholds are symmetric, i.e. $T_1=T_2$.  We find that the two-dimensional decision is as accurate as the one-dimensional decision.  That is, for a given expected time to reach a decision, the two-dimensional decision will reach the correct decision with the same probability.  Accuracy decreases as leak rates ($\ell$) become higher, but increases when the strength of the input ($c$) is higher (Figure \ref{2dacc}).

@@

\subsection{Increasing waiting costs make easy decisions take longer. }

If waiting is not costly and the error rate does not matter ($w_1=0$, $w_2=0$, $w_3=1$), there is no incentive for the individuals to stop accumulating evidence (fighting, in the social case) so the Nash equilibrium thresholds are high and both individuals wait until the other gives up.  However, as waiting costs increase, the pair can reach a decision more quickly if the weaker individual lowers its threshold.  If waiting costs are high enough, the stronger individual will also lower its threshold to avoid a long decision time (Figure \ref{nasheq_thresholds}).  Pairs making difficult decisions make more accurate decisions when the costs of waiting are higher since the weaker animal has an incentive to give up more quickly (Figure \ref{nasheq_thresholds}).  For low waiting costs, pairs of individuals making a difficult decision (low $c$, e.g. animals with similar fighting abilities) will take longer to reach a decision than pairs making a difficult decision (high $c$, e.g. animals with disparate fighting abilities).  At intermediate costs, pairs of individuals making intermediate decisions will take the longest to reach a decision.  When costs are high, the pairs that take the longest to reach a decision are those making the easiest decisions (Figure \ref{nasheq_thresholds}).

As with the Nash equilibrium thresholds, if waiting is not costly and the error rate does not matter ($w_1=0$, $w_2=0$, $w_3=1$), there is no incentive for the individuals to stop accumulating evidence (fighting, in the social case) so they will all set high thresholds.  As waiting costs increase, first weaker animals will start to lower their thresholds and then strong animals will as well (Figure \ref{groupeq_thresholds}).  For low waiting costs, pairs of animals with similar fighting abilities, and thus making difficult decisions, take the longest to reach a decision.  For high waiting costs, pairs of animals with similar and high fighting abilities take much longer, and those animals with similar and low fighting abilities will reach a decision more quickly.

\subsection{Costs affect the shape and the information content of the power distribution.  }

The average skewness of the power distribution is maximized at intermediate waiting costs ($w_2$) (Figure \ref{power}). Changing $w_1$ and $w_3$ have less of an effect, although when $w_1$ is higher the skewness slightly increases. The information content decreases as waiting costs increase.  Counterintuitively, if the individuals maximize the probability of being dominant in each of its pairs rather than the accuracy of those decisions, the information content of the power distribution increases (Figure \ref{power}).  In other words, the information in all of the group's decisions is higher when the accuracy of pairwise decisions decreases.

@@

\begin{figure}[ht]
\includegraphics[width=\textwidth]{2d_accuracy.pdf}
\caption{\label{2dacc} }
\end{figure}

\begin{figure}[ht]
\includegraphics[width=\textwidth]{2d_flexible_thresholds.pdf}
\caption{\label{2dflex} When the two thresholds in the two-dimensional system are allowed to vary freely, the decision process can be arbitrarily accurate in a given amount of time, depending on how much lower the weaker animal's threshold is than the stronger animal's threshold.  The expected time to reach a decision is on the x-axis and the probability of reaching the correct decision in that amount of time is on the y-axis.  The curve depends on the ratio of the weaker animal's threshold to the stronger animal's threshold ($\rho$).  Lower ratios are represented in higher darker curves.}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=\textwidth]{nasheq_thresholds.pdf}
\caption{\label{nasheq_thresholds} If a pair of individuals optimize their thresholds in response to each other, as the costs of waiting increase, first the weaker individual will start to lower his threshold to avoid waiting for a long time and then the stronger individual will start to lower his threshold as well.  As the costs of waiting increase, first the accuracy with which a pair can make a difficult decision increases and then it decreases.  At low waiting costs, difficult decisions take the most time.  At intermediate costs, intermediate decisions take the most time.  At high costs, easy decisions take the most time. The first row of panels shows the Nash equilibrium thresholds as a function of the difficulty of the decision ($c$ close to $.5$ is a more difficult decision).  The second and third rows show, respectively, the probability of the pair reaching the correct decision and the expected time until a decision is reached, if the pair of individuals uses the Nash equilibrium thresholds.  Each column corresponds to a particular waiting cost and the cost increases from left to right ($w_1=0, w_3=1-w_2$).  }
\end{figure}

\begin{figure}[ht]
\includegraphics[width=\textwidth]{groupeq_thresholds.pdf}
\caption{\label{groupeq_thresholds} If the animals optimize their thresholds with respect to the thresholds and fighting abilities of the whole group of animals, as the costs of fighting increase, first the weaker animals in the group lower their thresholds to avoid fighting for a long time with the stronger animals and then the stronger animals lower their thresholds as well.  The ability of to learn from an animal's signaling behavior decreases as the costs of fighting increase. When fighting is not costly, the pairs of animals that take longest to decide on a relationship are those with similar fighting abilities. As costs increase pairs of animals with similarly low fighting abilities resolve their relationships quickly, whereas pairs of animals with similarly high fighting abilities take a long time to resolve their relationships.  The first row of panels shows the optimal threshold as a function of the animal's true rank with respect to fighting ability.  The second row shows the mutual information between the probability of emitting a signal and the probability of being the weaker animal, as a function of the animal's true rank.  The third row shows the expected time until each pair of animals resolves their relationship.  Each column corresponds to a particular waiting cost and the cost increases from left to right ($w_1=0, w_3=1-w_2$).   }
\end{figure}

\begin{figure}[ht]
\begin{subfigure}{3.415in}
\caption{}
\includegraphics[width=\textwidth]{skewness_heatmap_poster.pdf}
\end{subfigure}
\begin{subfigure}{3.415in}
\caption{}
\includegraphics[width=\textwidth]{mutinfo_heatmap_poster.pdf}
\end{subfigure}
\caption{\label{power} Average skewness of the power distribution is maximized at intermediate waiting costs. The information content of the power distribution always increases as waiting costs decrease and when the benefits of being dominant increase.  The simplex shows the possible combinations of priorities, $w_1$, $w_2$, and $w_3$ such that the three weights sum to $1$.  In the lower left corner, $w_1=1$ (only accuracy matters), in the upper corner $w_2=1$ (only waiting time matters), and in the lower right $w_3=1$ (only the probability of receiving the signal matters).  The heatmaps show (a) the skewness of the power distribution and (b) the mutual information of the power distribution when the animals in the group optimize their thresholds according to those weights.  
%Increasing or decreasing $c_2$ has the strongest effect.  Increasing $c_1$ slightly increases the skewness. 
}
\end{figure}

\begin{table}[ht]
\centering
\caption{\label{variables}{\bf  Variables and interpretations in neural and social systems.} }
\ra{1.3}
\begin{tabular}{@{}rllll@{}}
Variable & Interpretation & Neural &   Social \\
\cmidrule{1-4} 
& input & dots moving left or right & fights won or lost
\\$c$ & strength of input & coherence of dots & probability of stronger animal winning
\\$X_1,X_2$ & decision variables &  firing rates of neural populations & opinions about relative dominance
\\ & dist. of states of the world & left / right equally likely & distribution of fighting abilities
\\ & decision & subject indicates left or right & one animal emits a subordination signal
\\ & correct decision & subject chooses correct direction & weaker animal signals
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{\label{models}{\bf  Comparison of models applied to neural and social systems.} Differences are highlighted in red.}
\ra{1.3}
\begin{tabular}{@{}rllll@{}}
& \multicolumn{2}{c}{Neural} &  Social \\
\cmidrule{2-3} \cmidrule{4-4} 
%model  & DDM or OU & race && race with leak
%\\
dimensionality & $1$  && $2$
\\decision & difference hits a threshold  && \fcolorbox{red}{white}{one var. hits a threshold}
\\ optimality criterion &  reward from being ``right" && reward from being ``right"
\\ & reward rate && reward rate
\\ & Bayes risk && Bayes risk
\\ & && \fcolorbox{red}{white}{reward from  receiving signal}
\\optimization depends on & input strength && input strength
\\ & noise && noise
\\ & leak rate && leak rate
\\ & && \fcolorbox{red}{white}{other animal's threshold}
\\threshold  algorithm & error correction
\\  & hill climbing
\end{tabular}
\end{table}
